%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[12pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.9,top=1cm, margin=2cm]{geometry}

%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


%\renewcommand*{\namefont}{\fontsize{42}{40}\mdseries\upshape}
% personal data
\firstname{Sourya}
\familyname{Kakarla}
\title{3rd Year CSE Undergraduate, IIT Kharagpur}           
\address{MW-304, M.S.Hall,IIT Kharagpur}{}    % optional, remove the line if not wanted
\mobile{(+918343997373)}                    % optional, remove the line if not wanted
\email{sourya4@gmail.com}                      % optional, remove the line if not wanted
\social[github]{ma08}
%\social[stackoverflow][stackoverflow.com/users/3465519/ma08]{ma08}
\homepage{ma08.github.io/about}                % optional, remove the line if not wanted
\extrainfo{\httplink[stackoverflow/ma08]{stackoverflow.com/users/3465519/ma08}} % optional, remove the line if not wanted

\newcommand\Mycventry[6]{%
\cventry{#1}{#2}{#3}{#4}{#5}{\fontsize{12}{15}\selectfont#6 }}
\renewcommand*\titlefont{\fontsize{15}{24}\selectfont}
\newcommand\Mycvline[2]{%
\cvline{#1}{\selectfont \fontfamily{\sfdefault}\fontsize{12}{15}\selectfont#2 }}
% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\vspace*{-2\baselineskip}
\maketitle
\vspace*{-1.5\baselineskip}
%\vspace*{-8mm}
\pagestyle{empty}


\section{Education}
\cventry{\textbf{2012--2017}}{Computer Science and Engineering (Dual Degree)}{}{IIT Kharagpur, W.B}{}{}
\cvline{CGPA:}{\small 8.69/10(at the end of 4th semester)}
\cventry{\textbf{2010--2012}}{Intermediate}{}{Sri Chaitanya Junior College, Hyderabad, Telangana}{}{}
\cvline{Aggregate:}{\small 94.7\%}
\cventry{\textbf{2010}}{Secondary School}{}{V.P.S Public School, Vijayawada, Andhra Pradesh}{}{}  % arguments 3 to 6 can be left empty
\cvline{CGPA:}{\small 10/10}


\section{Experience}

\Mycventry{2014}{Intern}{}{Advitech Infotech Pvt Ltd, Hyderabad, Telangana}{}{
\begin{description}
  \item[$\bullet$] Worked on \texttt{MEAN Stack} to develop a social webapp for professionals.
  \item[$\bullet$] Primarily worked on the server side - using \texttt{ node.js} and\texttt{ mongoDB}.
  \item[$\bullet$] Designed the database schemas on \texttt{mongoose} for \texttt{mongoDB} for the social network. 
  \item[$\bullet$] Used \texttt{Express.js} for url routing and \texttt{socket.io} for real time updates . 
  \item[$\bullet$] Implemented the connections part,  user groups and admin policy for groups, persistent and real time notifications. Worked on both the front-end and back-end.
  \item[$\bullet$] Implemented a chat server, newsfeed, and email service - was responsible for the back-end.
\end{description}
}

\section{Projects}
\Mycventry{2014}{Automated Restoration of Torn Documents}{}{Opensoft, IIT Kharagpur}{}{
\begin{description}
\item[$\bullet$] Team(of 7) secured bronze medal in the competition.
\item[$\bullet$] Used \texttt{openCV} on  \texttt{Python} for image processing.
\item[$\bullet$] Was primarily responsible for the GUI - implemented using \texttt{PyQt} - a \texttt{python} wrapper for \texttt{Qt}.
\item[$\bullet$] Implemented drag and drop functionality to upload and remove images, implemented animation effects for loading - using \texttt{PyQt}.
\item[$\bullet$] Back-end -  Implemented a function to calculate \texttt{Overlapping Area} of two polygons using \texttt{Polygon} module.
\item[$\bullet$] Github repo: \httplink{github.com/ma08/OpenSoft14}. 
\end{description}
}
\bigskip
\Mycventry{2014}{Chrome Link Copy}{}{A google chrome extension}{}{
\begin{description}
	\item[$\bullet$] Google Search results and links(sent/received) in Facebook Chat  are redirection urls. Using chrome's inbuilt \texttt{Copy Link Address} option, the redirection url is copied instead of the actual url the user intended to copy.
\item[$\bullet$] This extension is created to solve this problem by adding another option in the context menu - \texttt{Copy real link}. Using this option, the intended link is copied instead of the redirection url.
\item[$\bullet$] Built using  \texttt{JavaScript} and \texttt{jquery} in  \texttt{chrome's extension API}. Used  \texttt{regex} to extract the original url from the redirection urls \texttt{Facebook} and  \texttt{Google} create. 
\item[$\bullet$] Github repo: \httplink{github.com/ma08/chrome-link-copy}. 
\end{description}
}

%\bigskip
\Mycventry{2013}{CASE(Computer Aided Software Engineering) Tool}{}{Software Engineering Project}{}{
\begin{description}
\item[$\bullet$] Developed using \texttt{Java} for Software Engineering Course by a team of 2. A tool used to create(draw) data flow diagrams, modules, hierarchies etc.
\item[$\bullet$] Primarily used the \texttt{Swing} library to create the GUI to create the diagrams. 
\item[$\bullet$] Automatic generation of \texttt{Data Dictionary} and checking of \texttt{Balancing Error}. 
\item[$\bullet$] Implemented save and load operations for the diagrams using \texttt{Serialization}. 
\item[$\bullet$] Github repo: \httplink{github.com/ma08/CASE}. 
\end{description}
}

\bigskip
\section{Technical Experience}
\subsection{Proficient With}
\cvline{languages}{\texttt{C, C++, JavaScript, Python }}
\cvline{technologies}{\texttt{node.js, mongoDB, Vim, Git, socket.io,  Linux(Ubuntu) }}
\subsection{Have Experience With}
\cvline{languages}{\texttt{Java, Bash, Lua, VHDL }}
\cvline{technologies}{\texttt{GAS(GNU Assembler), Angular, \LaTeX{}, jekyll, gimp, Windows}}

\section{Relevant Coursework}
\Mycventry{}{IIT Kharagpur}{}{}{}{
Programming and Data Structures, Algorithms-1, Discrete Mathematics, Switching Circuits, Software Engineering, Signals and Systems, Probability and Statistics, Formal Languages and Automata Theory,
Compilers\textsuperscript{*}, Computer Organization and Architechture\textsuperscript{*}, Algorithms-2\textsuperscript{*}, Graph Theory\textsuperscript{*}  
\footnotesize{
\textsuperscript{*}To be completed before Dec 2014}
}


\section{Activities}
\Mycventry{2013--2014}{Football Team}{M.S.Hall}{IIT Kharagpur}{}{
Member of Gold Winning Team , M.S.Hall in the Sports General Championship.
}

\Mycventry{2012--2013}{Member, KGPian Game Theory Society}{IIT Kharagpur}{}{}{
Studied various aspects of Game Theory and its applications.
\begin{description}
	\item[$\bullet$] Published an article on  \texttt{Burning Bridges in the Football Transfer Market} in  \texttt{The Strategist}, the magazine of the society.
	\item[$\bullet$] Organized an event, \texttt{War of Wits} in IIT Kharagpur. Came up with the idea of the \texttt{Centipede Game} which hugely contributed to the success of the event.
\end{description}
}
\Mycventry{2008--2010}{Football Team}{V.P.S Public School}{}{}{
Part of school team in 9th and 10th class. Took part in an Interschool Tournament and reached the semifinals.
}

%\Mycventry{}{Other Current Hobbies}{}{}{}{
%Web Programming, Camping, Hiking, Backpacking, Traveling, Road Trips, Basketball, Piano, Guitar
%}

\end{document}
